Articles_Plots

### 2023-02-21 Articles.Rmd
Legend issues in SMSE for MLE

Theme_special<-function()
{
  theme(legend.key.width=unit(1,"cm"),
        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-1,-2,-1,-2)) 
}

>>>>

Theme_special<-function()
{
  theme(legend.key.width=unit(1,"cm"),
        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.box.margin=margin(0.2,0.4,0.4,0.3,"cm")#,
        #legend.margin=margin(0.2,0.4,0.4,0.3,"cm"),
        #plot.margin = margin(0.3,0.5,0.5,0.5,"cm")
        ) 
}
